### 2021-11-19 manuscript/document-package/coverletter/coverletter.tex

%@TheDoctorRAB
%Use for original, revised, clean manuscripts
\documentclass[11pt,a4paper]{article}
\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
\usepackage[pagewise]{lineno} %line numbering
\usepackage{setspace}
\usepackage{ulem} %strikethrough - do not \sout{\cite{}}
\usepackage[pdftex,dvipsnames]{xcolor,colortbl} %change font color
\usepackage{graphicx}
\usepackage{filecontents}
\usepackage{tablefootnote}
\usepackage{footnotehyper}
%\usepackage{subfig}
\usepackage[yyyymmdd]{datetime} %date format
\renewcommand{\dateseparator}{.}
\graphicspath{{../img/}} %path to graphics
\setcounter{secnumdepth}{5} %set subsection to nth level

@@

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{} %move page number to bottom right
%\renewcommand{\headrulewidth}{0pt} %set line thickness in header; uncomment as is to remove line
\lhead{\scriptsize }
\chead{\scriptsize \textit{- Draft Manuscript}}
\rhead{\scriptsize \today}
\rfoot{\thepage}

@@

\begin{titlepage}
    \title{Applying Analytic Hierarchy Process to Industrial Process Design in a Nuclear Renewable Hybrid Energy System}
    \author{
        , 
        , 
        \textsuperscript{*}
        \\ \\ \\
        \\

        \\ \\ \\
        \textsuperscript{*}
    }
\clearpage %not have page number on title page
\maketitle

\thispagestyle{empty} %start with page number 1 on second page
\end{titlepage}

\onehalfspacing %linespacing
\linenumbers %toggle line numbers
\pagewiselinenumbers %reset line numbers on new page
\modulolinenumbers[3] %line numbering interval

\nocite{*}

\bibliographystyle{standard}
\setlength{\bibhang}{0pt}
\bibliography{references}

>>>>

%TheDoctorRAB
%Used for first draft or revised manuscript
\documentclass[11pt,a4paper]{article}
\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
\usepackage[pagewise]{lineno} %line numbering
\usepackage{setspace}
\usepackage{ulem} %strikethrough - do not \sout{\cite{}}
\usepackage[pdftex,dvipsnames]{xcolor,colortbl} %change font color
\usepackage{graphicx}
\usepackage{filecontents}
\usepackage{tablefootnote}
\usepackage{footnotehyper}
%\usepackage{subfig}
\usepackage[yyyymmdd]{datetime} %date format
\renewcommand{\dateseparator}{.}
\graphicspath{{../img/}} %path to graphics
\setcounter{secnumdepth}{5} %set subsection to nth level

@@

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\rhead{
    \includegraphics[width=0.3\textwidth]{logo.png} \\
    \begin{scriptsize}
        1776 Science Center Drive \\
        Idaho Falls, ID 83402 \\
        208.282.7979 \\ 
    \end{scriptsize}
}

\cfoot{
    \begin{scriptsize}
        To enrich education through diversity, the University of Idaho is an equal opportunity/affirmative action employer.
    \end{scriptsize}
}

\rfoot{\thepage} %page number on bottom right

@@

\begin{flushright}
\noindent \\
\noindent \\
\noindent \textit{}\\
\end{flushright}

\hfill{\footnotesize\today}

\noindent Dear Dr. : \\

\noindent We would like to submit the original manuscript to \textit{} for peer review entitled, `'.

%\noindent (Each of the three reviewer comments were studied in detail, and a careful response was prepared for each comment. In the marked manuscript, omissions are recorded \sout{as follows}. For revisions, \edit{colored font was used}, and a footnote was provided to indicate the comment from the reviewer.\fn{R1 - Comment from Reviewer 1.})\\

\vspace{0.50\baselineskip}

\noindent Thank you again for the opportunity to publish in \textit{}.

\vspace*{\fill}
{\footnotesize
\begin{flushright}
    Sincerely, \\
    Prof. R. A. Borrelli \\
    University of Idaho $\sq$ Idaho Falls Center for Higher Education \\
    Department of Nuclear Engineering and Industrial Management \\
    Center for Advanced Energy Studies \\
    995 MK Simpson Boulevard, Idaho Falls ID 83401 \\
    rborrelli@uidaho.edu \\
    208.533.8122
    TheDoctorRAB.github.io
\end{flushright}
}
%\noindent \small{encl.: Marked Manuscript, Clean Manuscript, Response to Reviewer 1, Response to Reviewer 2, Response to Reviewer 3} %only major documents
\noindent {\footnotesize encl.: Draft Manuscript} %only major documents
